Supplemental information

### 2017-10-18 manuscript/CI_interactions.tex
added galler-parasitoid results to text.

      Using this prior distribution of galler-\emph{Salix} interaction frequencies, we can obtain parameters for the prior distribution of $\lambda$ in our dataset. Specifically, we obtain $\alpha$=2.807855, $\beta$=2.342815. We are then able to use these priors to estimate the posterior distriution of interaction probabilities given the additional information in our dataset.

@@

      For species where no co-occurances were observed, we can 
      calculate the MLE estimates for the mean and variance of 
      $\lambda_{ij}$ directly from this prior following 
      equations~\ref{mean} and~\ref{variance} 
      (see \emph{Appendix S2} for R implementation). The prior 
      distribution we obtain based on~\citet{Barbour2016,Barbour2016Dryad} is:
      $\hat{\lambda_{ij}}$=0.545, var($\lambda$)=0.048.
      This is consistent with the prior data, where the average 
      interaction probability based on the degree distributions of Salix genotypes and gallers was 0.541. [[What's the connectance of our dataset, if we call greys 0?]] This probability does, however, seem rather high for our dataset. This discrepancy may reflect the differences in scale between a network containing different genotypes of a single \emph{Salix} species and four gallers from a single family and a network containing many \emph{Salix} species and gallers from many families as is the case in our dataset.

      For a pair of species where some co-occurances were observed, we can update the prior distribution with these data. If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs. Thus $\alpha'$=$\alpha$ and $\beta'$=$\beta + n$. At the most extreme case, for a pair of species which co-occurred at all 374 sites and was never observed to interact, our distribution would become:

      $\hat{\lambda_{ij}}$=7.405645 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=1.938755 $\times$ 10$^{-5}$.

@@

      \begin{table}[h]
        \caption{95\% credible intervals for the interaction probability of two species that co-occur in $N$ sites but are never observed to interact, obtained using prior information from the \emph{Salix}-galler network in~\citet{Barbour2016,Barbour2016Dryad}.}
        \label{interval_table}
        \begin{tabular}{l | c c}
        N & Lower bound & Upper bound \\
        \hline
        0   & 0.157 & 0.901 \\
        2   & 0.099 & 0.743 \\
        4   & 0.072 & 0.621 \\
        6   & 0.057 & 0.530 \\
        8   & 0.047 & 0.462 \\
        10 & 0.040 & 0.408 \\
        14 & 0.031 & 0.331 \\
        20 & 0.023 & 0.258 \\
        30 & 0.016 & 0.188 \\
        40 & 0.012 & 0.148 \\
        50 & 0.010 & 0.122 \\
        \hline
        374 & 0.001 & 0.018 \\
        \hline
        \end{tabular}
        \end{table}

@@

      Rather than calculating confidence intervals for a posterior distribution after collecting data, we may wish to know how many data points are necessary to obtain a given level of confidence that two co-occurring species do not interact. The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact. If we want to be 95\% confident that the interaction probability for two species in the \emph{Salix}-galler system is below 0.5, 0.1, or 0.01, we would need six, 54, and 114 observed co-occurrances with no observed interaction (Fig.~\ref{Salix_cdfs}; see function samples\_required in~\emph{Appendix S2}). Given the low levels of replication in most network studies, this implies that we should have fairly low confidence in many "non-interacting" pairs of species. Even in the extensively replicated \emph{Salix}-galler dataset very few species pairs were observed co-occurring frequently enough to reach these thresholds (173/4992 pairs were observed at least six times, two pairs were observed at least 54 times, and no pair was observed more than 114 times). Discounting potential interactions, then, requires either a stronger prior expectation of no interaction (e.g., we can be highly confident that a palm tree will not predate upon a leopard no matter how many times the two species are observed together) or very extensive sampling.

>>>>

      Using this prior distribution of galler-\emph{Salix} interaction frequencies, we can obtain parameters for the prior distribution of $\lambda$ in our dataset. Specifically, we obtain $\alpha$=2.807855, $\beta$=2.342815. For the galler-parasitoid component of the network, the corresponding prior parameters are $\alpha$=1.341479, $\beta$=9.487966.
      We are then able to use these priors to estimate the posterior distriution of interaction probabilities given the additional information in our dataset.

@@

      For species where no co-occurances were observed, we can 
      calculate the MLE estimates for the mean and variance of 
      $\lambda_{ij}$ directly from this prior following 
      equations~\ref{mean} and~\ref{variance} 
      (see \emph{Appendix S2} for R implementation). The prior 
      distribution we obtain based on~\citet{Barbour2016,Barbour2016Dryad} is:
      $\hat{\lambda_{ij}}$=0.545, var($\lambda$)=0.048 for the \emph{Salix}-galler network and $\hat{\lambda_{ij}}$=0.124, var($\lambda$)=0.010 for the galler-parasitoid network.
      This is consistent with the prior data, where the average 
      interaction probability based on the degree distributions of Salix genotypes and gallers was 0.541 and that for gallers and parasitoids was 0.122. [[What's the connectance of our dataset, if we call greys 0?]] This probability does, however, seem rather high for our dataset. This discrepancy may reflect the differences in scale between a network containing different genotypes of a single \emph{Salix} species and four gallers from a single family and a network containing many \emph{Salix} species and gallers from many families as is the case in our dataset.

      For a pair of species where some co-occurances were observed, we can update the prior distribution with these data. If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs. Thus $\alpha'$=$\alpha$ and $\beta'$=$\beta + n$. At the most extreme case, for a pair of species which co-occurred at all 374 sites and was never observed to interact, our distributions would become:

      $\hat{\lambda_{ij}}$=7.405645 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=1.938755 $\times$ 10$^{-5}$ for the \emph{Salix}-galler network and 
      $\hat{\lambda_{ij}}$=3.485906 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=9.026737 $\times$ 10$^{-6}$ for the galler-parasitoid network.

@@

      \begin{table}[h]
        \caption{95\% credible intervals for the interaction probability of two species that co-occur in $N$ sites but are never observed to interact, obtained using prior information from the \emph{Salix}-galler network in~\citet{Barbour2016,Barbour2016Dryad}.}
        \label{interval_table}
        \begin{tabular}{l | c c | c c }
        \multirow{2}{*}{N} & \multicolumn{2}{c}{\emph{Salix}-galler} & \multicolumn{2}{c}{galler-parasitoid}\\
         & Lower bound & Upper bound \\
        \hline
        0   & 0.157 & 0.901 & 0.008 & 0.364 \\
        2   & 0.099 & 0.743 & 0.006 & 0.313 \\
        4   & 0.072 & 0.621 & 0.006 & 0.274 \\
        6   & 0.057 & 0.530 & 0.005 & 0.244 \\
        8   & 0.047 & 0.462 & 0.004 & 0.219 \\
        10  & 0.040 & 0.408 & 0.004 & 0.200 \\
        14  & 0.031 & 0.331 & 0.003 & 0.169 \\
        20  & 0.023 & 0.258 & 0.003 & 0.137 \\
        30  & 0.016 & 0.188 & 0.002 & 0.104 \\
        40  & 0.012 & 0.148 & 0.002 & 0.084 \\
        50  & 0.010 & 0.122 & 0.001 & 0.071 \\
        \hline                  
        374 & 0.001 & 0.018 & \textless0.001 & 0.011 \\
        \hline
        \end{tabular}
        \end{table}

@@

      Rather than calculating confidence intervals for a posterior distribution after collecting data, we may wish to know how many data points are necessary to obtain a given level of confidence that two co-occurring species do not interact. The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact. If we want to be 95\% confident that the interaction probability for two species in the \emph{Salix}-galler network is below 0.5, 0.1, or 0.01, we would need six, 54, and 114 observed co-occurrances with no observed interaction (Fig.~\ref{Salix_cdfs}; see function samples\_required in~\emph{Appendix S2}). 
      Although the prior distribution of interaction probabilities is narrower and closer to zero for the galler-parasitoid network, the number of samples required to be 95\% confident that the interaction probability is below a threshold still increases quickly; we would need 25 and 101 observed co-occurances with no observed interaction for threshold interaction probabilities of 0.1 and 0.01, respectively.
      Given the low levels of replication in most network studies, this implies that we should have fairly low confidence in many "non-interacting" pairs of species. Even in the extensively replicated \emph{Salix}-galler dataset very few species pairs were observed co-occurring frequently enough to reach these thresholds (173/4992 pairs were observed at least six times, two pairs were observed at least 54 times, and no pair was observed more than 114 times). Discounting potential interactions, then, requires either a stronger prior expectation of no interaction (e.g., we can be highly confident that a palm tree will not predate upon a leopard no matter how many times the two species are observed together) or very extensive sampling.

### 2017-10-18 manuscript/supplemental.tex
added galler-parasitoid results to text.

      \vspace{12pt}
      \emph{
      \noindent \hspace{-4pt} \# Now get the degree distributions from the web\\
      deg\_dist\_Salix=rowSums(prior\_web)/ncol(prior\_web)\\
      \# Remove one genotype that never interacted\\
      deg\_dist\_Salix\textless-deg\_dist\_Salix[which(rowSums(prior\_web)\textgreater0)]\\
      deg\_dist\_galler=colSums(prior\_web)/nrow(prior\_web)\\
      \# Interaction probabilities are the product of plant and galler probabilities\\
      int\_probs=as.numeric(deg\_dist\_galler\%$*$\%t(deg\_dist\_Salix))\\
      }

@@

>>>>

      \vspace{12pt}
      \emph{
      \noindent \hspace{-4pt} \# Now get the degree distributions from the web\\
      deg\_dist\_Salix=rowSums(prior\_web)/ncol(prior\_web)\\
      \# Remove one genotype that never interacted\\
      deg\_dist\_Salix\textless-deg\_dist\_Salix[which(rowSums(prior\_web)\textgreater0)]\\
      deg\_dist\_galler=colSums(prior\_web)/nrow(prior\_web)\\
      \# Interaction probabilities are the product of plant and galler probabilities\\
      int\_probs=as.numeric(deg\_dist\_galler\%$*$\%t(deg\_dist\_Salix))\\

      \# And for the galler-parasitoid web:\\
      deg\_dist\_parasitoid=rowSums(prior\_web\_para\_only)/ncol(prior\_web\_para\_only)\\
      deg\_dist\_parasitized=colSums(prior\_web\_para\_only)/nrow(prior\_web\_para\_only)\\
      gp\_int\_probs=as.numeric(deg\_dist\_parasitized\%$*$\%t(deg\_dist\_parasitoid))

      }

@@

      % deg_dist_parasitoid=rowSums(prior_web_para_only)/ncol(prior_web_para_only)
      % deg_dist_parasitized=colSums(prior_web_para_only)/nrow(prior_web_para_only)
      % gp_int_probs=deg_dist_parasitized%*%t(deg_dist_parasitoid)
